GeoSPARQL 1.1: an almost decadal update to the most important geospatial LOD standard

### 2021-04-21 manuscript.tex
tiny wording change

In parallel, the OGC API Features standard \cite{ogcapifeaturespart3} is developed, which also proposes functions for filtering feature collections. Even though, OGC API Features proposes the use of the Common Query Language (CQL) for filtering, it is open to other query language implementations such as GeoSPARQL. When comparing the filter capabilities of CQL to GeoSPARQL, one can observe that concerning spatial filter capabilities, the two query languages provide comparable functionality. However, the version of CQL proposed by OGC API Features also provides support of spatiotemporal operators, which may be an addition to be further explored in the contiuous GeoSPARQL development process.

>>>>

In parallel, the OGC API Features standard \cite{ogcapifeaturespart3} is developed, which also proposes functions for filtering feature collections. While OGC API Features proposes the use of the Common Query Language (CQL) for filtering, it is also open to other query language implementations such as GeoSPARQL. When comparing the filter capabilities of CQL to GeoSPARQL, one can observe that concerning spatial filter capabilities, the two query languages provide comparable functionality. However, the version of CQL proposed by OGC API Features also provides support of spatiotemporal operators, which may be an addition to be further explored in the contiuous GeoSPARQL development process.
